### 2022-12-09 dissertation/appendix/symbols.tex
✨ (symbols): Chapters 3,4,7 done

\begin{description}
	\item
	      [\parbox{1cm}{$\alpha$}] Control parameter for leaky ReLU that controls non-zero gradients. (See Eq.~\eqref{eq:an_function_mapping} p.~\pageref{eq:an_function_mapping})
\end{description}

@@

@@

@@

@@

@@

>>>>

\begin{description}
	% \item
	%       [\parbox{2cm}{$EXAMPLE$}] THIS IS AN EXAMPLE DESCRIPTION. \lbrack Eq.~\eqref{eq:an_function_mapping} pg.~\pageref{eq:an_function_mapping} \rbrack

	\item [\parbox{2cm}{$I$}] The input pattern's dimension size.
	\item [\parbox{2cm}{$T$}] The target pattern's dimension size.
	\item [\parbox{2cm}{$\mathbb{R}$}] The real-number space.
	\item [\parbox{2cm}{$\mathbb{R}^{I}$}] The real-number space in I dimensions.
	\item [\parbox{2cm}{$\mathbb{R}^{T}$}] The real-number space in T dimensions.
	\item [\parbox{2cm}{$f_{AN}$}] The mapping function realised by the \acs{AN}.
	\item [\parbox{2cm}{$\boldsymbol{x}$}] The input pattern/vector.
	\item [\parbox{2cm}{$x_{i}$}] The $i$-th dimension of the input pattern/vector.
	\item [\parbox{2cm}{$\theta$}] The bias unit.
	\item [\parbox{2cm}{$\boldsymbol{v}$}] The weight vector.
	\item [\parbox{2cm}{$v_{i}$}] The $i$-th dimension of the weight vector.
	\item [\parbox{2cm}{$net$}] The net input signal to the \acs{AN}.
	\item [\parbox{2cm}{$f(net)$}] The activation function over net input signal.
	\item [\parbox{2cm}{$\boldsymbol{y}$}] The output vector.
	\item [\parbox{2cm}{$\boldsymbol{y}_{p}$}] The output vector for pattern $p$.
	\item [\parbox{2cm}{$k$}] Index for the output vector.
	\item [\parbox{2cm}{$x_{i,p}^{'}$}] The normalised form of the input at dimension $i$, pattern $p$.
	\item [\parbox{2cm}{$x_{i,p}$}] The original input at dimension $i$, pattern $p$.
	\item [\parbox{2cm}{$x_{i_{min}}$}] The input's minimum value at dimension $i$.
	\item [\parbox{2cm}{$x_{i_{max}}$}] The input's maximum value at dimension $i$.
	\item [\parbox{2cm}{$p$}] Index for the input data patterns.
	\item [\parbox{2cm}{$P$}] Total number of input data patterns.
	\item [\parbox{2cm}{$\boldsymbol{x}_p$}] The $p$-th input vector/pattern.
	\item [\parbox{2cm}{$\mu_i$}] The mean of the input at dimension $i$.
	\item [\parbox{2cm}{$\sigma^2_i$}] The unit variance of the input at dimension $i$.
	\item [\parbox{2cm}{$i$}] Index for the input vector.
	\item [\parbox{2cm}{$\omega$}] The general weight vector used for normalisation.
	\item [\parbox{2cm}{$\omega_{i}$}] The general weight vector used for normalisation at dimension $i$.
	\item [\parbox{2cm}{$\omega_{min}$}] The lower bound of the uniform distribution used for weights initialisation.
	\item [\parbox{2cm}{$\omega_{max}$}] The upper bound of the uniform distribution used for weights initialisation.
	\item [\parbox{2cm}{$fanin$}] The number of input neurons to the weight vector.
	\item [\parbox{2cm}{$fanout$}] The number of output neurons from the weight vector.
	\item [\parbox{2cm}{$\sigma$}] The standard deviation of the truncated normal distribution used for weight initialisation.
	\item [\parbox{2cm}{$K$}] Number of output units.
	\item [\parbox{2cm}{$x_{i+1}$}] The $i+1$-th dimension of the input pattern/vector.
	\item [\parbox{2cm}{$v_{i+1}$}] The $i+1$-th dimension of the weight vector.
	\item [\parbox{2cm}{$net^{'}$}] The augmented net input signal that includes the bias term.
	\item [\parbox{2cm}{$\tau$}] Phase shift threshold parameter.
	\item [\parbox{2cm}{$f(x)$}] The function used to describe the \acs{LReLU} activation function.
	\item [\parbox{2cm}{$f$}] A shorted form of the activation function.
	\item [\parbox{2cm}{$x^{+}$}] The positive part of the input parameter's domain.
	\item [\parbox{2cm}{$\alpha$}] Scaling parameter used by the \acs{LReLU} activation function.
	\item [\parbox{2cm}{$\lambda$}] Scaling/control parameter used by the sigmoid and tanh activation functions.
	\item [\parbox{2cm}{$x_{min}$}] The input's minimum value used by the min-max scaler.
	\item [\parbox{2cm}{$x_{max}$}] The input's maximum value used by the min-max scaler.
	\item [\parbox{2cm}{$\mathbb{R}^{K}$}] The real-number space in $K$ dimensions.
	\item [\parbox{2cm}{$y_{k}$}] The $k$-th dimension of the output vector.
	\item [\parbox{2cm}{$y^{'}_k$}] The softmax value of the output at dimension $k$.
	\item [\parbox{2cm}{$\boldsymbol{y^{'}}$}] The softmax form of the output vector.
	\item [\parbox{2cm}{$h_{j}$}] The $j$-th dimension of the hidden layer.
	\item [\parbox{2cm}{$j$}] Index used for the hidden layer.
	\item [\parbox{2cm}{$v_{i,j}$}] The weight associated with input node $x_{i}$ and the hidden node $h_{j}$.
	\item [\parbox{2cm}{$w_{j,k}$}] The weight associated with hidden node $h_{j}$ and the output node $y_{k}$.
	\item [\parbox{2cm}{$net_{i,h}$}] The net input signal at the hidden layer.
	\item [\parbox{2cm}{$net_{h,y}$}] The net input signal at the output layer.
	\item [\parbox{2cm}{$\epsilon$}] The cost/loss produced by the loss function.
	\item [\parbox{2cm}{$y_{k,p}$}] The output produced by the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
	\item [\parbox{2cm}{$\hat{y}_{k,p}$}] The target output for the \acs{ANN} at the $k$-th dimension for the $p$-th pattern.
	\item [\parbox{2cm}{$\beta$}] Mini-batch size.
	\item [\parbox{2cm}{$\mathbbm{1}$}] The indicator function.
	\item [\parbox{2cm}{$c$}] Index used for $c$-th class.
	\item [\parbox{2cm}{$C$}] Total number of classes.

\end{description}

@@

\begin{description}
	\item [\parbox{2cm}{$f$}] A shortened form of the objective function being optimised.
	\item [\parbox{2cm}{$x$}] The independent variables to the objective function. Also used in \acs{DE} notation to denote the selection mechanism for the trial vector.
	\item [\parbox{2cm}{$f(x)$}] The objective function over $x$.
	\item [\parbox{2cm}{$\epsilon$}] The error between the output of the \acs{FFNN} and the target pattern, produced by the loss function. Also used as a small error value used by heuristics to avoid division by 0.
	\item [\parbox{2cm}{$\mathcal{E}$}] The error function.
	\item [\parbox{2cm}{$w_{i}(t)$}] The $i$-th dimension of the weight vector at time step $t$.
	\item [\parbox{2cm}{$w_{i}(t-1)$}] The $i$-th dimension of the weight vector at time step $t-1$.
	\item [\parbox{2cm}{$\Delta w_{i}(t)$}] The change in the $i$-th dimension of the weight vector at time step $t$.
	\item [\parbox{2cm}{$w_{i}$}] The $i$-th dimension of the weight vector.
	\item [\parbox{2cm}{$i$}] Index used for the weight vector. Also used as the index for the $i$-th particle in the population, implemented by \acs{PSO}.
	\item [\parbox{2cm}{$\boldsymbol{w}$}] The weight vector.
	\item [\parbox{2cm}{$p$}] Index used for input data patterns.
	\item [\parbox{2cm}{$o_{i,p}$}] The $i$-th dimension of the output for pattern $p$.
	\item [\parbox{2cm}{$t_{i,p}$}] The $i$-th dimension of the target for pattern $p$.
	      item [\parbox{2cm}{$o_{k,p}$}] The $k$-th dimension of the output for pattern $p$.
	\item [\parbox{2cm}{$t_{k,p}$}] The $k$-th dimension of the target for pattern $p$.
	\item [\parbox{2cm}{$net_{p}$}] The net input signal for pattern $p$.
	\item [\parbox{2cm}{$z_{i,p}$}] The input value at index $i$ for pattern $p$.
	\item [\parbox{2cm}{$\boldsymbol{g}$}] General symbol used to represent the gradient vector, retrieved from the error function relative to the weight vector.
	\item [\parbox{2cm}{$\boldsymbol{v}$}] The velocity vector resulting from \acs{Momentum}.
	\item [\parbox{2cm}{$\boldsymbol{w}$}] General symbol used to represent the weight vector.
	\item [\parbox{2cm}{$\epsilon_{T}$}] The error at time step $T$.
	\item [\parbox{2cm}{$\epsilon_{T_{p}}$}] The error produced for pattern $p$ at time step $T$.
	\item [\parbox{2cm}{$\eta$}] Learning rate.
	\item [\parbox{2cm}{$k$}] Index used for the output layer.
	\item [\parbox{2cm}{$K$}] Total number of output units.
	\item [\parbox{2cm}{$t$}] Time step.
	\item [\parbox{2cm}{$T$}] Time step.
	\item [\parbox{2cm}{$\alpha$}] The momentum hyper-parameter.
	\item [\parbox{2cm}{$w_{t,i}$}] The $i$-th dimension of the weight vector at time step $t$.
	\item [\parbox{2cm}{$w_{t+1,i}$}] The $i$-th dimension of the weight vector at time step $t+1$.
	\item [\parbox{2cm}{$G_{t,ii}$}] Diagonal matrix containing the sum of the squared gradients with regards to the $i$-th dimension of the weight vector.
	\item [\parbox{2cm}{$g_{t,i}$}] The $i$-th dimension of the gradient vector at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{G_{t}}$}] The sum of the squares of the gradients.
	\item [\parbox{2cm}{$G_{t,i}$}] The sum of the squared gradients with regards to the $i$-th dimension of the weight vector.
	\item [\parbox{2cm}{$\odot$}] The matrix-vector product.
	\item [\parbox{2cm}{$W$}] Window size of previous squared gradients.
	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t}$}] The expected value of the squared gradients at time step $t$.
	\item [\parbox{2cm}{$E[\boldsymbol{g}^{2}]_{t - 1}$}] The expected value of the squared gradients at time step $t-1$.
	\item [\parbox{2cm}{$\boldsymbol{g}^{2}_{t}$}] The squared gradient vector at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{w}_{t+1}$}] The weight vector at time step $t+1$.
	\item [\parbox{2cm}{$\boldsymbol{w}_{t}^{2}$}] The squared weight vector at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{g}_{t}$}] The gradient vector at time step $t$.
	\item [\parbox{2cm}{$RMS$}] The root mean squared error criterion.
	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t}$}] The expected value of the delta of the squared weight vector at time step $t$.
	\item [\parbox{2cm}{$E[\Delta \boldsymbol{w}^{2}]_{t - 1}$}] The expected value of the delta of the squared weight vector at time step $t-1$.
	\item [\parbox{2cm}{$\Delta \boldsymbol{w}^{2}_{t}$}] The delta of the squared weight vector at time step $t$.
	\item [\parbox{2cm}{$RMS[\Delta \boldsymbol{w}]_{t}$}] The root mean squared delta of the weight vector at time step $t$.
	\item [\parbox{2cm}{$RMS[\Delta \boldsymbol{w}]_{t-1}$}] The root mean squared delta of the weight vector at time step $t-1$.
	\item [\parbox{2cm}{$RMS[\boldsymbol{g}]_{t}$}] The root mean squared gradient vector at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{g}_{t}$}] The gradient vector at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{m}_{t}$}] The estimate of the first moment at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{m}_{t+1}$}] The estimate of the first moment at time step $t+1$.
	\item [\parbox{2cm}{$\boldsymbol{v}_{t}$}] The estimate of the second moment at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{v}_{t+1}$}] The estimate of the second moment at time step $t+1$.
	\item [\parbox{2cm}{$\beta_{1}$}] First decay rate parameter for \acs{Adam}.
	\item [\parbox{2cm}{$\beta_{2}$}] Second decay rate parameter for \acs{Adam}.
	\item [\parbox{2cm}{$\hat{\boldsymbol{m}}_{t}$}] The bias-corrected first moment at time step $t$.
	\item [\parbox{2cm}{$\hat{\boldsymbol{v}}_{t}$}] The bias-corrected second moment at time step $t$.
	\item [\parbox{2cm}{$\beta^{t}_{1}$}] First decay rate parameter for \acs{Adam} at time step $t$.
	\item [\parbox{2cm}{$\beta^{t}_{2}$}] Second decay rate parameter for \acs{Adam} at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] The $i$-th particle's position vector as implemented by \acs{PSO}. Also represents the $i$-th parent's position vector as implemented by \acs{DE}.
	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(t)$}] The $i$-th particle's position vector at time step $t$ as implemented by \acs{PSO}. Also represents the $i$-th parent's position vector at time step $t$ as implemented by \acs{DE}.
	\item [\parbox{2cm}{$\boldsymbol{v}_{i}(t)$}] The $i$-th particle's velocity vector at time step $t$ as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$f(x_{i})$}] The evaluation of the $i$-th particle's solution with respect to the objective function.
	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(t)$}] The $i$-th particle's personal best position vector at time step $t$ as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$\boldsymbol{x}_{i}(0)$}] The $i$-th particle's position vector at time step $0$ as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$\boldsymbol{y}_{i}(0)$}] The $i$-th particle's personal best position vector at time step $0$ as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}_{i}(t)$}] The $i$-th particle's global best position vector as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$\boldsymbol{x}_{i}$}] The $i$-th particle's position vector as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$\boldsymbol{x}_{min}$}] The lower bound constraint vector of the position vector's values.
	\item [\parbox{2cm}{$\boldsymbol{x}_{max}$}] The upper bound constraint vector of the position vector's values.
	\item [\parbox{2cm}{$v_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the velocity vector at time step $t+1$.
	\item [\parbox{2cm}{$v_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the velocity vector at time step $t$. Also used in the mutation operator for \acp{GA} to represent some sampled mutation update value.
	\item [\parbox{2cm}{$w$}] The inertia weight hyper-parameter as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$c_{1}$}] The cognitive control parameter as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$c_{2}$}] The social control parameter as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$r_{1_{j}}(t)$}] The $j$-th dimension of the first stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$r_{2_{j}}(t)$}] The $j$-th dimension of the second stochastic scaling parameter at time step $t$ as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$x_{ij}$}] The $i$-th particle's/entity's $j$-th dimension of the position vector.
	\item [\parbox{2cm}{$x_{ij}(t)$}] The $i$-th particle's/entity's $j$-th dimension of the position vector at time step $t$.
	\item [\parbox{2cm}{$y_{ij}$}] The $i$-th particle's $j$-th dimension of the personal best position vector.
	\item [\parbox{2cm}{$y_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the personal best position vector at time step $t$.
	\item [\parbox{2cm}{$\boldsymbol{\hat{y}}$}] Short form of the global best position vector.
	\item [\parbox{2cm}{$\hat{y}_{ij}$}] The $i$-th particle's $j$-th dimension of the global best position vector.
	\item [\parbox{2cm}{$\hat{y}_{ij}(t)$}] The $i$-th particle's $j$-th dimension of the global best position vector at time step $t$.
	\item [\parbox{2cm}{$f(\hat{y})$}] The evaluation of the global best position.
	\item [\parbox{2cm}{$x_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the position vector at time step $t+1$.
	\item [\parbox{2cm}{$\boldsymbol{r}_{1}$}] The vector for the first stochastic scaling parameter as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$\boldsymbol{r}_{2}$}] The vector for the second stochastic scaling parameter as implemented by \acs{PSO}.
	\item [\parbox{2cm}{$I$}] The total number of particles in the swarm (particle swarm size).
	\item [\parbox{2cm}{$N$}] An alternative to the particle swarm size.
	\item [\parbox{2cm}{$j$}] Index used for the dimensions of candidate solutions.
	\item [\parbox{2cm}{$J$}] The total number of dimensions in the position vector for particles in \acs{PSO}.
	\item [\parbox{2cm}{$U$}] The uniform distribution.
	\item [\parbox{2cm}{$v'_{ij}(t+1)$}] The $i$-th particle's $j$-th dimension of the clamped velocity vector at time step $t+1$.
	\item [\parbox{2cm}{$\boldsymbol{V}_{max}$}] The upper bound of the velocity clamping vector.
	\item [\parbox{2cm}{$V_{max,j}$}] The $j$-th dimension of the upper bound of the velocity clamping vector.
	\item [\parbox{2cm}{$\boldsymbol{u}_{i}(t)$}] The $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.
	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{1}}(t)$}] The $i$-th entity's target vector at time step $t$ implemented by \acs{DE}.
	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{2}}(t)$}] The $i$-th entity's first selected individual's position vector at time step $t$ implemented by \acs{DE}.
	\item [\parbox{2cm}{$\boldsymbol{x}_{i_{3}}(t)$}] The $i$-th entity's second selected individual's position vector at time step $t$ implemented by \acs{DE}.
	\item [\parbox{2cm}{$i_{1}$}] Index for the target vector in \acs{DE}.
	\item [\parbox{2cm}{$i_{2}$}] Index for the first selected individual in \acs{DE}.
	\item [\parbox{2cm}{$i_{3}$}] Index for the second selected individual in \acs{DE}.
	\item [\parbox{2cm}{$\beta$}] Scale factor as implemented by \acs{DE}.
	\item [\parbox{2cm}{$\boldsymbol{x}'_{i}(t)$}] The $i$-th offspring's position vector at time step $t$ as implemented by \acs{DE}.
	\item [\parbox{2cm}{$x'_{ij}(t)$}] The $i$-th offspring's $j$-th dimension of the position vector at time step $t$.
	\item [\parbox{2cm}{$u_{ij}(t)$}] The $j$-th dimension of the $i$-th entity's trial vector at time step $t$ implemented by \acs{DE}.
	\item [\parbox{2cm}{$\mathcal{J}$}] The set of crossover points.
	\item [\parbox{2cm}{$j^{*}$}] Randomly selected crossover point.
	\item [\parbox{2cm}{$\emptyset$}] The empty set.
	\item [\parbox{2cm}{$p_{r}$}] The crossover probability i.e. recombination probability.
	\item [\parbox{2cm}{$f(\boldsymbol{x}_{i}(t))$}] The evaluation of the $i$-th entity's candidate solution at time step $t$.
	\item [\parbox{2cm}{$f(\boldsymbol{x}'_{i}(t))$}] The evaluation of the $i$-th offspring's candidate solution at time step $t$.
	\item [\parbox{2cm}{$f(\boldsymbol{y}_{i})$}] The evaluation of the $i$-th particle's personal best position.
	\item [\parbox{2cm}{$f(\boldsymbol{\hat{y}})$}] The evaluation of the global best position.
	\item [\parbox{2cm}{$x_{min,j}$}] The $j$-th dimension of the lower bound constraint for an entity's position.
	\item [\parbox{2cm}{$x_{max,j}$}] The $j$-th dimension of the upper bound constraint for an entity's position.
	\item [\parbox{2cm}{$\mathcal{C}$}] The set of entities in the population.
	\item [\parbox{2cm}{$\mathcal{C}(0)$}] The set of entities in the population at time step $0$.
	\item [\parbox{2cm}{$\mathcal{C}(t)$}] The set of entities in the population at time step $t$.
	\item [\parbox{2cm}{$\mathcal{C}(t+1)$}] The set of entities in the population at time step $t+1$.
	\item [\parbox{2cm}{$y$}] Used in \acs{DE} notation to denote the number of difference vectors to include.
	\item [\parbox{2cm}{$z$}] Used in \acs{DE} notation to denote the type of crossover operator to use.
	\item [\parbox{2cm}{$p_{c}$}] Probability of producing offspring.
	\item [\parbox{2cm}{$p_{x}$}] Bitswapping probability.
	\item [\parbox{2cm}{$m_{j}(t)$}] The $j$-th dimension of the crossover mask, $m$, at time step $t$.
	\item [\parbox{2cm}{$p_{m}$}] The mutation probability.
	\item [\parbox{2cm}{$N_{t}$}] Tournament selection size.
\end{description}

@@

\begin{description}
	\item [\parbox{2cm}{$K$}] The number of folds to execute for $K$-fold crossover validation.
\end{description}

@@

\begin{description}
	\item [\parbox{2cm}{$\alpha_{0}$}]
	\item [\parbox{2cm}{$\alpha_{1}$}]
	\item [\parbox{2cm}{$\alpha_{k}$}]
	\item [\parbox{2cm}{$\alpha_{K}$}]
	\item [\parbox{2cm}{$\alpha$}]
	\item [\parbox{2cm}{$\bar{A}$}]
	\item [\parbox{2cm}{$\beta'$ }]
	\item [\parbox{2cm}{$\beta$}]
	\item [\parbox{2cm}{$Bin$}]
	\item [\parbox{2cm}{$\boldsymbol{\alpha'}$}]
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{2cm}{$\boldsymbol{\mathcal{D}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{2cm}{$\boldsymbol{N}$}]
	\item [\parbox{2cm}{$\boldsymbol{x_{1}}$}]
	\item [\parbox{2cm}{$\boldsymbol{x_{i}}$}]
	\item [\parbox{2cm}{$\boldsymbol{x_{I}}$}]
	\item [\parbox{2cm}{$\boldsymbol{x}$}]
	\item [\parbox{2cm}{$\boldsymbol{X}$}]
	\item [\parbox{2cm}{$\boldsymbol{Y}$}]
	\item [\parbox{2cm}{$\emptyset$}]
	\item [\parbox{2cm}{$\Gamma'(n)$}]
	\item [\parbox{2cm}{$\Gamma(n)$}]
	\item [\parbox{2cm}{$\Gamma$}]
	\item [\parbox{2cm}{$\mathbb{R}$}]
	\item [\parbox{2cm}{$\mathbbm{1}$}]
	\item [\parbox{2cm}{$\mathcal{A}$}]
	\item [\parbox{2cm}{$\mathcal{L}$}]
	\item [\parbox{2cm}{$\overset{\text{iid}}{\sim}$}]
	\item [\parbox{2cm}{$\psi$}]
	\item [\parbox{2cm}{$\theta_{1}$}]
	\item [\parbox{2cm}{$\theta_{k}$}]
	\item [\parbox{2cm}{$\theta_{K}$}]
	\item [\parbox{2cm}{$\theta$}]
	\item [\parbox{2cm}{$A$}]
	\item [\parbox{2cm}{$B_{1}$}]
	\item [\parbox{2cm}{$B_{2}$}]
	\item [\parbox{2cm}{$B_{i}$}]
	\item [\parbox{2cm}{$B_{j}$}]
	\item [\parbox{2cm}{$B_{K}$}]
	\item [\parbox{2cm}{$B(\boldsymbol{\alpha})$}]
	\item [\parbox{2cm}{$B$}]
	\item [\parbox{2cm}{$Ber(\theta)$}]
	\item [\parbox{2cm}{$Beta$}]
	\item [\parbox{2cm}{$Bin$}]
	\item [\parbox{2cm}{$c$}]
	\item [\parbox{2cm}{$Cat$}]
	\item [\parbox{2cm}{$d$}]
	\item [\parbox{2cm}{$Dir$}]
	\item [\parbox{2cm}{$dn$}]
	\item [\parbox{2cm}{$E[{x_{k}}]$}]
	\item [\parbox{2cm}{$E[\ln(x_{k})]$}]
	\item [\parbox{2cm}{$E[\ln(x)]$}]
	\item [\parbox{2cm}{$E[x_{k}]$}]
	\item [\parbox{2cm}{$E[x]$}]
	\item [\parbox{2cm}{$f_{Ber}$}]
	\item [\parbox{2cm}{$f_{Beta}$}]
	\item [\parbox{2cm}{$f_{Bin}$}]
	\item [\parbox{2cm}{$f_{Cat}$}]
	\item [\parbox{2cm}{$f_{Dir}$}]
	\item [\parbox{2cm}{$f_{Mul}$}]
	\item [\parbox{2cm}{$f$}]
	\item [\parbox{2cm}{$F$}]
	\item [\parbox{2cm}{$g^{*}$}]
	\item [\parbox{2cm}{$g$}]
	\item [\parbox{2cm}{$i$}]
	\item [\parbox{2cm}{$I$}]
	\item [\parbox{2cm}{$j$}]
	\item [\parbox{2cm}{$K$}]
	\item [\parbox{2cm}{$k$}]
	\item [\parbox{2cm}{$K$}]
	\item [\parbox{2cm}{$M[x_{k}]$}]
	\item [\parbox{2cm}{$M[x]$}]
	\item [\parbox{2cm}{$m$}]
	\item [\parbox{2cm}{$M$}]
	\item [\parbox{2cm}{$Mul$}]
	\item [\parbox{2cm}{$N_{0}$}]
	\item [\parbox{2cm}{$N_{1}$}]
	\item [\parbox{2cm}{$N_{k}$}]
	\item [\parbox{2cm}{$N_{K}$}]
	\item [\parbox{2cm}{$n$}]
	\item [\parbox{2cm}{$N$}]
	\item [\parbox{2cm}{$p$}]
	\item [\parbox{2cm}{$S$}]
	\item [\parbox{2cm}{$v$}]
	\item [\parbox{2cm}{$x_{1}$}]
	\item [\parbox{2cm}{$x_{i,k}$}]
	\item [\parbox{2cm}{$x_{i}$}]
	\item [\parbox{2cm}{$x_{I}$}]
	\item [\parbox{2cm}{$x_{j}$}]
	\item [\parbox{2cm}{$x_{k}$}]
	\item [\parbox{2cm}{$x_{K}$}]
	\item [\parbox{2cm}{$x$}]
	\item [\parbox{2cm}{$y_{1}$}]
	\item [\parbox{2cm}{$Y_{1}$}]
	\item [\parbox{2cm}{$y_{2}$}]
	\item [\parbox{2cm}{$Y_{2}$}]
	\item [\parbox{2cm}{$y_{i}$}]
	\item [\parbox{2cm}{$Y_{i}$}]
	\item [\parbox{2cm}{$y_{n}$}]
	\item [\parbox{2cm}{$Y_{N}$}]
\end{description}

@@

\begin{description}
	\item [\parbox{2cm}{$\alpha_{1}$}]
	\item [\parbox{2cm}{$\alpha_{k}$}]
	\item [\parbox{2cm}{$\alpha_{K}$}]
	\item [\parbox{2cm}{$\alpha$}]
	\item [\parbox{2cm}{$\beta_{1}$}]
	\item [\parbox{2cm}{$\beta_{2}$}]
	\item [\parbox{2cm}{$\beta_{j,k}$}]
	\item [\parbox{2cm}{$\beta_{K}^{J}$}]
	\item [\parbox{2cm}{$\beta$}]
	\item [\parbox{2cm}{$\boldsymbol{\alpha}$}]
	\item [\parbox{2cm}{$\boldsymbol{\beta}$}]
	\item [\parbox{2cm}{$\boldsymbol{\gamma}$}]
	\item [\parbox{2cm}{$\boldsymbol{\hat{\phi}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\hat{\psi}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\hat{\theta}}$}]
	\item [\parbox{2cm}{$\boldsymbol{\lambda}$}]
	\item [\parbox{2cm}{$\boldsymbol{\phi}$}]
	\item [\parbox{2cm}{$\boldsymbol{\psi}$}]
	\item [\parbox{2cm}{$\boldsymbol{\theta}$}]
	\item [\parbox{2cm}{$\boldsymbol{C}$}]
	\item [\parbox{2cm}{$\boldsymbol{E}$}]
	\item [\parbox{2cm}{$\boldsymbol{H}$}]
	\item [\parbox{2cm}{$\epsilon(-1)$}]
	\item [\parbox{2cm}{$\epsilon$}]
	\item [\parbox{2cm}{$\eta$}]
	\item [\parbox{2cm}{$\gamma_{0}$}]
	\item [\parbox{2cm}{$\gamma_{1,k}$}]
	\item [\parbox{2cm}{$\gamma_{1}$}]
	\item [\parbox{2cm}{$\gamma_{2,k}$}]
	\item [\parbox{2cm}{$\gamma_{K}$}]
	\item [\parbox{2cm}{$\hat{\phi}_{j,k}$}]
	\item [\parbox{2cm}{$\hat{\psi_{k}}$}]
	\item [\parbox{2cm}{$\hat{\psi}_{k}$}]
	\item [\parbox{2cm}{$\hat{\theta_{k}}$}]
	\item [\parbox{2cm}{$\hat{\theta}_{k}$}]
	\item [\parbox{2cm}{$\lambda_{1}$}]
	\item [\parbox{2cm}{$\lambda_{j}$}]
	\item [\parbox{2cm}{$\lambda_{J}$}]
	\item [\parbox{2cm}{$\mathbbm{1}_{0}$}]
	\item [\parbox{2cm}{$\mathbbm{1}_{1}$}]
	\item [\parbox{2cm}{$\mathbin{\%}$}]
	\item [\parbox{2cm}{$\mathcal{A}(v)$}]
	\item [\parbox{2cm}{$\mathcal{L}$}]
	\item [\parbox{2cm}{$\phi_{j,k}$}]
	\item [\parbox{2cm}{$\phi_{jk}$}]
	\item [\parbox{2cm}{$\phi$}]
	\item [\parbox{2cm}{$\psi_{k}$}]
	\item [\parbox{2cm}{$\psi_{k}N_{k}$}]
	\item [\parbox{2cm}{$\psi$}]
	\item [\parbox{2cm}{$\theta_{k}$}]
	\item [\parbox{2cm}{$\theta$}]
	\item [\parbox{2cm}{$A$}]
	\item [\parbox{2cm}{$B$}]
	\item [\parbox{2cm}{$Beta$}]
	\item [\parbox{2cm}{$Bin$}]
	\item [\parbox{2cm}{$c_{1}$}]
	\item [\parbox{2cm}{$c_{i,k}$}]
	\item [\parbox{2cm}{$c_{i}$}]
	\item [\parbox{2cm}{$Dir$}]
	\item [\parbox{2cm}{$e_{i,j,k}$}]
	\item [\parbox{2cm}{$e_{i}$}]
	\item [\parbox{2cm}{$e_{j}$}]
	\item [\parbox{2cm}{$E[\phi_{j,k}]$}]
	\item [\parbox{2cm}{$E[\psi_{k}]$}]
	\item [\parbox{2cm}{$E[\theta_{k}]$}]
	\item [\parbox{2cm}{$h_{i,k}$}]
	\item [\parbox{2cm}{$h_{i}$}]
	\item [\parbox{2cm}{$h_{k}$}]
	\item [\parbox{2cm}{$i$}]
	\item [\parbox{2cm}{$I$}]
	\item [\parbox{2cm}{$j$}]
	\item [\parbox{2cm}{$J$}]
	\item [\parbox{2cm}{$K-1$}]
	\item [\parbox{2cm}{$k$}]
	\item [\parbox{2cm}{$K$}]
	\item [\parbox{2cm}{$L$}]
	\item [\parbox{2cm}{$LSE$}]
	\item [\parbox{2cm}{$Mult$}]
	\item [\parbox{2cm}{$N_{0,k}$}]
	\item [\parbox{2cm}{$N_{1,k}$}]
	\item [\parbox{2cm}{$N_{j,k}$}]
	\item [\parbox{2cm}{$N_{j}$}]
	\item [\parbox{2cm}{$N_{k}$}]
	\item [\parbox{2cm}{$N$}]
	\item [\parbox{2cm}{$S$}]
	\item [\parbox{2cm}{$t$}]
\end{description}

@@

\begin{description}
	\item [\parbox{2cm}{$\alpha$}] Used as a scaling parameter for the \acs{LReLU} activation function. Also used as a threshold parameter for the statistical significance tests.
	\item [\parbox{2cm}{$\eta$}] Learning rate.
	\item [\parbox{2cm}{$\mathbb{R}$}] Real-number space.
	\item [\parbox{2cm}{$v_{ij}$}] The $j$-th dimension of the velocity vector of the $i$-th particle in the population implemented by \acs{PSO}.
	\item [\parbox{2cm}{$x_{ij}$}] The $j$-th dimension of the position vector of the $i$-th particle in the population implemented by \acs{PSO}.
\end{description}
